14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Benchmark scoring.

A solver's \emph{parallel performance} for each benchmark is a quadruple $\langle
e, n, w, c\rangle$, with $e \in \{0, 1\}$ the number of erroneous
results (usually~$e = 0$), $0 \leq n \leq N$ the number of correct
results,\footnote{Here, $N$ is the number of \akey{check-sat} commands
  in the benchmark.  Recall that \maintrack benchmarks have just one
  \akey{check-sat} command; incremental track benchmarks may have
  multiple \akey{check-sat} commands.} $w \in [0,T]$ the (real-valued)
wall-clock time in seconds, and $c \in [0, 4T]$ the (real-valued) CPU
time in seconds, measured across all cores and sub-processes, until
the solver process terminates.

\header{\maintrack.} More specifically, for the \maintrack, we have
%
\begin{itemize}
\item $e=0$, $n=0$ if the solver aborts without a response, or the
  result of the \akey{check-sat} command is \texttt{unknown},
\item $e=0$, $n=1$ if the result of the \akey{check-sat} command is
  \texttt{sat} or \texttt{unsat}, and the result either agrees with
  the benchmark status or the benchmark status is unknown,\footnote{If
    the benchmark status is unknown, we thus treat the solver's answer
    as correct.  Disagreements between different solvers on benchmarks
    with unknown status are governed in
    Section~\ref{sec:division-scoring}.}
\item $e=1$, $n=0$ if the result of the \akey{check-sat} command is
  incorrect.
\end{itemize}
%
Note that a (correct or incorrect) response is taken into
consideration even when the solver process terminates abnormally, or
does not terminate within the time limit.  Solvers should take care
not to accidentally produce output that contains \texttt{sat} or
\texttt{unsat}.

\header{Incremental Track.}
%
An application benchmark may contain multiple \akey{check-sat}
commands.  Solvers may partially solve the benchmark before timing
out.  The benchmark is run by the trace executor, measuring the total
time (summed over all individual commands) taken by the solver to
respond to commands.\footnote{Times measured by StarExec may include
  time spent in the trace executor.  We expect that this time will
  likely be insignificant compared to time spent in the solver, and
  nearly constant across solvers.}  Most time will likely be spent in
response to \akey{check-sat} commands, but \akey{assert}, \akey{push}
or \akey{pop} commands might also entail a reasonable amount of
processing.  For the incremental track, we have
\begin{itemize}
\item $e=1$, $n=0$ if the solver returns an incorrect result for any
  \akey{check-sat} command within the time limit,
\item otherwise, $e=0$, and $n$ is the number of correct results for
  \akey{check-sat} commands returned by the solver before the time
  limit is reached.
\end{itemize}

\header{\ucoretrack.}
%
For the \ucoretrack, we instead have $0 \leq n \leq A$, where~$A$
is the number of named top-level assertions in the benchmark, and
\begin{itemize}
\item $e=0$, $n=0$ if the solver aborts without a response, or the
  result of the \akey{check-sat} command is \texttt{unknown},
\item $e=1$, $n=0$ if the result is erroneous according to
  Section~\ref{sec:exec:unsat-core},
\item otherwise, $e=0$, and $n$ is the reduction in the number of
  formulas, i.e., $n = A$ minus the number of formula names in the
  reported unsatisfiable core.
\end{itemize}

\subsection{Sequential Performance (\maintrack)}
\label{sec:sequential}

\iffalse
SMT-COMP has traditionally emphasized sequential performance (i.e.,
CPU time) over parallel performance (i.e., wall-clock time).  StarExec
measures both, and we intend to recognize both best sequential and
best parallel solvers in all competitive \maintrack divisions.
\fi

The parallel performance, as defined in Section~\ref{sec:benchmark-scoring},
favors parallel solvers, which may utilize all available processor
cores.  To evaluate sequential performance, we derive a
\emph{sequential performance} by imposing a (virtual) CPU time limit equal
to the wall-clock time limit~$T$.  A solver result is taken into
consideration for the sequential performance only if the solver process
terminates within this CPU time limit.  More specifically, for a given
parallel performance $\langle e, n, w, c\rangle$, the corresponding sequential
performance is defined as~$\langle e_S, n_S, c_S\rangle$, where
\begin{itemize}
\item $e_S = 0$ and $n_S = 0$ if $c > T$, $e_S = e$ and $n_S = n$
  otherwise,
\item $c_S = \min\ \{c, T\}$.\footnote{\emph{Rationale:} Under this
  measure, a solver should not benefit from using multiple processor
  cores.  Conceptually, the sequential performance should be (nearly)
  unchanged if the solver was run on a single-core processor, up to a
  time limit of~$T$.}
\end{itemize}

>>>>

The \textbf{parallel benchmark score} of a solver is a quadruple $\langle
e, n, w, c\rangle$, with
\begin{itemize}[noitemsep]
  \vspace{-1ex}
  \item \makebox[5em][l]{$e \in \{0, 1\}$}
    number of erroneous results (usually~$e = 0$)
  \item \makebox[5em][l]{$0 \leq n \leq N$}
    number of correct results (resp.~\emph{reduction} for the \ucoretrack)
  \item \makebox[5em][l]{$w \in [0,T]$}
    wall-clock time in seconds (real-valued)
  \item \makebox[5em][l]{$c \in [0, 4T]$}
    CPU time in seconds (real-valued)
\end{itemize}

\header{Error Score ($\mathbf{e}$).}
For the \maintrack, \inctrack and \challtrack, $e$ is the number of returned
statuses that disagree with the given expected status (as described above,
disagreements on benchmarks with unknown status lead to the benchmark being
disregarded). For the \ucoretrack, $e$ includes, in addition, the number of
returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as
validated by a selection of other solvers selected by organizers).  For the
\mvaltrack, $e$ includes, in addition, the number of returned models that are
ill-formed or not full satisfiable models.

\header{Correctly Solved Score ($\mathbf{n}$).}
For the \maintrack, \inctrack, \challtrack and \mvaltrack,
$N$ is defined as the number of \akey{check-sat} commands, and
$n$ is defined as the number of correct results.
For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
and the size of the unsat core.

\header{Wall-Clock Time Score ($\mathbf{w}$).}
The (real-valued) wall-clock time in seconds, until time limit $T$ or the
solver process terminates.

\header{CPU Time Score ($\mathbf{c}$).}
The (real-valued) CPU time in seconds, measured across all cores and
sub-processes, until time limit $4T$ or the solver process terminates.

\subsubsection{Sequential Benchmark Score}
\label{sec:sequential}

The parallel score as defined above favors parallel solvers, which may utilize
all available processor cores.  To evaluate sequential performance, we derive a
\emph{sequential score} by imposing a (virtual) CPU time limit equal to the
wall-clock time limit~$T$.  A solver result is taken into consideration for the
sequential score only if the solver process terminates within this CPU time
limit.  More specifically, for a given parallel performance $\langle e, n, w,
c\rangle$, the corresponding sequential performance is defined as~$\langle e_S,
n_S, c_S\rangle$, where
\begin{itemize}
\item $e_S = 0$ and $n_S = 0$ if $c > T$, and $e_S = e$ and $n_S = n$
  otherwise,
\item $c_S = \min\ \{c, T\}$.\footnote{Under this
  measure, a solver should not benefit from using multiple processor
  cores.  Conceptually, the sequential performance should be (nearly)
  unchanged if the solver was run on a single-core processor, up to a
  time limit of~$T$.}
\end{itemize}

\subsubsection{\maintrack and \challtrack.}
  For the \maintrack and \challtrack, the error score $e$ and the correctly
  solved score $n$ are defined as
  \begin{itemize}
  \item $e=0$ and $n=0$ if the solver
    \begin{itemize}[noitemsep,nolistsep]
      \item aborts without a response, or
      \item  the result of the \akey{check-sat} command is \texttt{unknown},
    \end{itemize}
  \item $e=0$ and $n=1$ if the result of the \akey{check-sat} command is
      \texttt{sat} or \texttt{unsat} and either
    \begin{itemize}[noitemsep,nolistsep]
      \item agrees with the benchmark status,
      \item or the benchmark status
        is unknown,\footnote{If the benchmark status is unknown, we thus treat
        the solver's answer as correct.  Disagreements between different
        solvers on benchmarks with unknown status are governed in
        Section~\ref{sec:division-scoring}.}
    \end{itemize}
  \item $e=1$ and $n=0$ if the result of the \akey{check-sat} command is
    incorrect.
  \end{itemize}
%
Note that a (correct or incorrect) response is taken into
consideration even when the solver process terminates abnormally, or
does not terminate within the time limit.  Solvers should take care
not to accidentally produce output that contains \texttt{sat} or
\texttt{unsat}.

\subsubsection{Incremental Track.}
%
An application benchmark may contain multiple \akey{check-sat}
commands.  Solvers may partially solve the benchmark before timing
out.  The benchmark is run by the trace executor, measuring the total
time (summed over all individual commands) taken by the solver to
respond to commands.\footnote{Times measured by StarExec may include
  time spent in the trace executor.  We expect that this time will
  likely be insignificant compared to time spent in the solver, and
  nearly constant across solvers.}  Most time will likely be spent in
response to \akey{check-sat} commands, but \akey{assert}, \akey{push}
or \akey{pop} commands might also entail a reasonable amount of
processing.  For the \inctrack, we have
\begin{itemize}
\item $e=1$ and $n=0$ if the solver returns an incorrect result for any
  \akey{check-sat} command within the time limit,
\item otherwise, $e=0$ and $n$ is the number of correct results for
  \akey{check-sat} commands returned by the solver before the time
  limit is reached.
\end{itemize}

\subsubsection{\ucoretrack.}
  For the \ucoretrack, the error score $e$ and the correctly solved score $n$
  are defined as
  \begin{itemize}
  \item $e=0$ and $n=0$ if the solver
    \begin{itemize}[noitemsep,nolistsep]
      \item aborts without a response, or
      \item the result of the \akey{check-sat} command is \texttt{unknown},
    \end{itemize}
  \item $e=1$and  $n=0$ if the result is erroneous according to
    Section~\ref{sec:exec:unsat-core},
  \item otherwise, $e=0$ and $n$ is the \emph{reduction} in the number of
    formulas, i.e., $n = N$ minus the number of formula names in the
    reported unsatisfiable core.
  \end{itemize}
